Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2020-09-30 summary.Rmd
results from mod max

```{r clust_err_k, fig.cap = 'IQR of clustering error using Algorithm 2 (red) compared against subspace clustering (blue) for sample sizes from 64 to 2048 and number of clusters from 2 to 8. Simulations were repeated 100 times for each sample size. The $y$-axis is shown on a logarithmic scale.', fig.width = 8}
clustering.df <- readr::read_csv('clustering-k.csv')
clustering.df %>%
  dplyr::group_by(K, n) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75)) %>%
  dplyr::ungroup() %>% 
  ggplot() +
  scale_y_log10() +
  # scale_x_log10() + 
  labs(y = '1 - adjusted rand index', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err,
                colour = 'Algorithm 2')) +
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q,
                    colour = 'Algorithm 2')) + 
  geom_line(aes(x = n, y = med.err.ssc,
                colour = 'SSC')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc, ymax = third.q.ssc,
                    colour = 'SSC')) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both')
```

@@

```{r, cache = FALSE, fig.cap = 'Adjacency matrix of the Karnataka villages data, arranged by the clustering produced by Algorithm 2.', fig.height = 2}
hh <- readRDS('data/village-hh-59.rds')
A.hh <- hh$A
z.hh <- hh$z
K <- 6
zhat.hh <- cluster.pabm(A.hh, K, 
                        use.all = TRUE, normalize = FALSE, p = K, q = 0)

>>>>

```{r clust_err_k, fig.cap = 'IQR of clustering error using Algorithm 2 (red) compared against subspace clustering (green) and modularity maximization (blue) for sample sizes from 64 to 2048 and number of clusters from 2 to 8. Simulations were repeated 100 times for each sample size. The $y$-axis is shown on a logarithmic scale.', fig.width = 8}
clustering.df <- readr::read_csv('clustering-k.csv')
mod.max.df <- readr::read_csv('mod-max-k.csv') %>% 
  dplyr::group_by(K, n) %>% 
  dplyr::summarise(med.err.mm = median(error.mm),
                   first.q.mm = quantile(error.mm, .25),
                   third.q.mm = quantile(error.mm, .75)) %>% 
  dplyr::ungroup()
clustering.df %>%
  dplyr::group_by(K, n) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75)) %>%
  dplyr::ungroup() %>% 
  ggplot() +
  scale_y_log10() +
  # scale_x_log10() + 
  labs(y = '1 - adjusted rand index', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err,
                colour = 'Algorithm 2')) +
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q,
                    colour = 'Algorithm 2')) + 
  geom_line(aes(x = n, y = med.err.ssc,
                colour = 'SSC')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc, ymax = third.q.ssc,
                    colour = 'SSC')) + 
  geom_line(data = mod.max.df,
            aes(x = n, y = med.err.mm,
                colour = 'modularity maximization')) + 
  geom_errorbar(data = mod.max.df,
                aes(x = n, ymin = first.q.mm, ymax = third.q.mm,
                    colour = 'modularity maximization')) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both')
```

@@

```{r, cache = FALSE, fig.cap = 'Adjacency matrix of the Karnataka villages data, arranged by the clustering produced by Algorithm 2 (left) and results of \\citet{fosdick2016multiresolution} (right).', fig.height = 2}
hh <- readRDS('data/village-hh-59.rds')
A.hh <- hh$A
z.hh <- hh$z
K <- 6
zhat.hh <- cluster.pabm(A.hh, K, 
                        use.all = TRUE, normalize = FALSE, p = K, q = 0)
